Case study validations of automatic bullet matching

### 2018-11-26 index.Rmd
phrasing change

More explicit characterization of bullet surfaces has been discussed since at least 1958 (\citeauthor{davis1968introduction}), but at the time technology was not sufficiently advanced to make an analysis based on 3D measurements or surface traces a viable option. \citet{ComputerIdentificationBullets1978} demonstrated use of a scanning electron microscope to quantitatively examine and compare bullet striae. More recently, approaches using 3D measurement data were explicitly described in 1999 (\citeauthor{dekinderAutomatedComparisonsBullet1999}), and have been further developed by \citet{bachrachDevelopment3DbasedAutomated2002,xieAutomatedBulletidentificationSystem2009, chuPilotStudyAutomated2010}. These approaches utilize 3D surface measurements directly to characterize the topology of land engraved areas (LEAs), rather than using visual or image comparison techniques. In many cases, these approaches also provide some level of automation of the comparison process, with the goal of reducing human biases by augmenting the visual information with 3D measurements. Utilizing the 3D measurements allows for examination of both peaks and valleys in LEAs, \hh{it also allows us to take the depth of striae into account, something that is difficult, if not impossible, for visual examination.}

>>>>

More explicit characterization of bullet surfaces has been discussed since at least 1958 (\citeauthor{davis1968introduction}), but at the time technology was not sufficiently advanced to make an analysis based on 3D measurements or surface traces a viable option. \citet{ComputerIdentificationBullets1978} demonstrated use of a scanning electron microscope to quantitatively examine and compare bullet striae. More recently, approaches using 3D measurement data were explicitly described in 1999 (\citeauthor{dekinderAutomatedComparisonsBullet1999}), and have been further developed by \citet{bachrachDevelopment3DbasedAutomated2002,xieAutomatedBulletidentificationSystem2009, chuPilotStudyAutomated2010}. These approaches utilize 3D surface measurements directly to characterize the topology of land engraved areas (LEAs), rather than using visual or image comparison techniques. In many cases, these approaches also provide some level of automation of the comparison process, with the goal of reducing human biases by augmenting the visual information with 3D measurements. Utilizing the 3D measurements allows for examination of both peaks and valleys in LEAs, \hh{it also allows us to take the depth of striae into account, something that is difficult, if not impossible,} \svp{from} \hh{visual examination.}
